Comparison of Analytical and Artificial Neural Network models in predicting hot deformation behavior of AISI P20

### 2022-11-25 Article.tex
Move misplaced Tables labels

The material used in this study is the modified carbon alloy AISI P20 whose chemical composition is given in Table \ref{tab:Composition}.
\begin{table}[h!]
\centering
\caption{Chemical composition of AISI P20 steel, Fe = balance.}
\begin{tabular}{lccccccc}
	\hline
	Element &  C   &  Mn  &  Mo  &  Si  &  Ni  &  Cr  &  Cu  \\ \hline
	Wt~\%   & 0.30 & 0.89 & 0.52 & 0.34 & 0.68 & 1.86 & 0.17 \\ \hline
	\label{tab:Composition}
\end{tabular}
\end{table}
Cylindrical samples were machined with an initial diameter of $d=10$~mm and a height of $h_0=15$~mm.
A batch of 30 hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the 5 temperature levels of $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$ with the 6 strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/Gleeble-3800}
\caption{The Gleeble-3800 thermomechanical simulator system used for this study}
\label{fig:Gleeble3800}
\end{figure}
Thin tantalum sheets were used as a lubricating material at the contact surface of the anvils and samples to minimize friction during testing.
As shown in Figure \ref{fig:GleebleProcess}, the samples were heated to a temperature of $1260\celsius$ with a heating rate of $2$\celsius/s and held at this temperature for $5$~min to eliminate thermal gradients.
They were then cooled down with a rate of $1$\celsius/s to the test temperature and then held at constant temperature for $1$~min before deformation.
During the compression phase, the temperature of the specimen is kept constant by the thermal control system of the machine.
After compression, the specimen is quickly quenched to freeze its microstructure for later analysis.
Figure \ref{fig:GleebleProcess} also shows the aspects of the specimens before and after the compression test: $h_0$ and $r_0$ are the height and radius before compression and $h$, $r_m$ and $r_t$ are the height, large radius and small radius of the specimen after compression, respectively.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.8\columnwidth]{Figures/GleebleProcess}
\caption{Schematic diagram of the experimental process.}
\label{fig:GleebleProcess}
\end{figure}

@@

\begin{table}[h!]
\centering
\caption{Parameters' values of the Johnson-Cook flow law for the P20 steel.}
\begin{tabular}{ccccc}
\hline
$A~(\text{MPa})$ & $B~(\text{MPa})$ & $n$ & $C$ & $m$\\
$13.5143$&$21.816$&$0.0746$&$0.3404$&$0.7057$\\\hline
\label{tab:JC}
\end{tabular}
\end{table}

@@

By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$.
The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively.
Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right),
\end{equation}
with $S_2=C_5+C_6\left(T-T_0\right)$.
Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot\varepsilon/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$.
The parameters of MZA model are given in Table \ref{tab:MZA} while its prediction are plotted in Figure \ref{fig:CompExp-MZA-6}.
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Modified-Zerilli-Armstrong Model}
\begin{tabular}{ccccccc}
\hline
$C_1$ & $C_2$ & $C_3$ & $C_4$ & $C_5$ & $C_6$ & $n$\\
$13.5143$ & $21.2591$ & $4.7902\times 10^{-3}$ & $1.4895\times 10^{-4}$ & $0.1389$ & $1.495\times 10^{-4}$ & $0.0621$\\
\hline
\label{tab:MZA}
\end{tabular}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/CompExp-MZA-6}
\caption{Comparison between the experimental and predicted flow stresses by MZA model}
\label{fig:CompExp-MZA-6}
\end{figure}
It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates.
The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation.
For the MZA model, $\AARE=21.20~\%$ and $\RMSE=19.57~\text{MPa}$, this shows an overall worse performance than the JC model as reported in \cite{TizeMha-2022}.

@@

\begin{table}[h!]
\centering
\caption{Parameters' values of the Hansel-Spittel flow law for the P20 steel.}
\begin{tabular}{ccccc}
\hline
$A$ & $m_1$ & $m_2$ & $m_3$ & $m_4$\\
$5.954\times 10^{3}$ & $-3.3576\times10^{-3}$ & $0.2641$ & $-0.0868$ & $2.2688\times10^{-4}$\\\hline
& $m_5$ & $m_6$ & $m_7$ & $m_8$\\
& $-4.2163\times10^{-4}$ & $-0.0561$ & $2.264\times10^{-4}$ & $0$\\\hline
\label{tab:HS}
\end{tabular}
\end{table}

@@

The determination of the order $m$ of the polynomials defined by Equations (\ref{eq:ArA}-\ref{eq:Arn}) is defined according to the ability of the model to represent the non-linear dependence of the stress versus the strain and its generalization.
The values $\ln\!A_i$, $\alpha_i$, $n_i$, and $Q_i$ ($i=0,1,2,3,\cdots,m$) are the coefficients of the polynomials to determine using a regression method.
Setting $m=9$ gives the best results and the corresponding parameters are reported in Table \ref{tab:AR}.
\begin{table}[h!]
\centering
\caption{Parameters' values of the Arrhenius flow law for the P20 steel.}
\begin{tabular}{llll}
\hline
\multicolumn{1}{c}{$\alpha_i$} & \multicolumn{1}{c}{$Q_i~(\times 10^{-6})$} & \multicolumn{1}{c}{$\ln\!A_i$} & \multicolumn{1}{c}{$n_i$}\\
\hline
$\alpha_0=0.0407$ & $Q_0=0.467$ & $A_0=35.8092$ & $n_0=4.8217$\\
$\alpha_1=-0.5167$ & $Q_1=-0.6517$ & $A_1=-58.822$ & $n_1=3.2814$\\
$\alpha_2=6.3912$ & $Q_2=7.6084$ & $A_2=740.3303$ & $n_2=71.5963$\\
$\alpha_3=-47.3364$ & $Q_3=-48.016$ & $A_3=-5.0493\times 10^{3}$ & $n_3=-1.9562\times 10^{3}$\\
$\alpha_4=220.0014$ & $Q_4=66.795$ & $A_4=1.1305\times 10^{4}$ & $n_4=1.4461\times 10^{4}$\\
$\alpha_5=-654.4553$ & $Q_5=468.8898$ & $A_5=2.022\times 10^{4}$ & $n_5=-5.431\times 10^{4}$\\
$\alpha_6=1.2421\times 10^{3}$ & $Q_6=-2.3032\times 10^{3}$ & $A_6=-1.5387\times 10^{5}$ & $n_6=1.1761\times 10^{5}$\\
$\alpha_7=-1.4523\times 10^{3}$ & $Q_7=4.3707\times 10^{3}$ & $A_7=3.1798\times 10^{5}$ & $n_7=-1.4882\times 10^{5}$\\
$\alpha_8=952.0619$ & $Q_8=-3.9394\times 10^{3}$ & $A_8=-2.9725\times 10^{5}$ & $n_8=1.0239\times 10^{5}$\\
$\alpha_9=-267.4994$ & $Q_9=1.397\times 10^{3}$ & $A_9=1.0759\times 10^{5}$ & $n_9=-2.9621\times 10^{4}$\\
\hline
\label{tab:AR}
\end{tabular}
\end{table}
This modified form of the Arrhenius behavior law allows for accurate and reliable prediction over a wide range of temperatures and strain rates.
Equation (\ref{eq:ArStress}) is finally used to compute the flow stress $\sigma^y$ from the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$:
\begin{equation}
\sigma^y = \frac{1}{\alpha(\varepsilon)} \ln\left\{\left(\frac{\mdot\varepsilon \exp{\left(\frac{Q(\varepsilon)}{RT}\right)}}{A(\varepsilon)}\right)^{\frac{1}{n(\varepsilon)}} + \left[1 + \left(\frac{\mdot\varepsilon \exp{\left(\frac{Q(\varepsilon)}{RT}\right)}}{A(\varepsilon)}\right)^{\frac{2}{n(\varepsilon)}}\right]^{\frac{1}{2}}\right\}
\label{eq:ArStress}
\end{equation}

@@

\begin{table}[h!]
\centering
\caption{Parameters' values of the PTM flow law for the P20 steel.}
\begin{tabular}{llll}
	\hline
	\multicolumn{1}{c}{$A_i$}  & \multicolumn{1}{c}{$B_i$}   & \multicolumn{1}{c}{$C_0^i$} & \multicolumn{1}{c}{$C_1^i$}   \\ \hline
	$A_0=16.8529$              & $B_0=-3.5418\times 10^{-3}$ & $C_0^0=0.1608$              & $C_1^0=-1.9037\times 10^{-5}$ \\
	$A_1=340.6451$             & $B_1=-0.0132$               & $C_0^1=-0.6202$             & $C_1^1=2.67\times 10^{-3}$    \\
	$A_2=-1.9594\times 10^{3}$ & $B_2=-4.4888\times 10^{-3}$ & $C_0^2=4.9516$              & $C_1^2=-3.5788\times 10^{-3}$ \\
	$A_3=4.836\times 10^{3}$   & $B_3=0.2218$                & $C_0^3=-13.1694$            & $C_1^3=-0.0222$               \\
	$A_4=-5.5176\times 10^{3}$ & $B_4=-0.4988$               & $C_0^4=15.25$               & $C_1^4=0.0609$                \\
	$A_5=2.4058\times 10^{3}$  & $B_5=0.3211$                & $C_0^5=-6.587$              & $C_1^5=-0.0413$               \\ \hline
	\label{tab:PTM}
\end{tabular}
\end{table}

@@

A summary of the coefficients for evaluating the high-temperature flow stress prediction capability of the AISI P20 alloy for all models presented in this work is reported in Table \ref{tab:Errors}.
\begin{table}[h!]
\centering
\caption{Accuracy coefficients for all the analyzed models.}
\begin{tabular}{lcccccc}
\hline
Coefficients & JC & MZA & HS & AR & PTM & ANN\\
\hline
$\AARE(\%)$ & $14.05$ & $21.20$ & $7.75$ & $3.56$ & $4.79$ & $0.62$\\
$\RMSE(\text{MPa})$ & $12.00$ & $19.57$ & $3.80$ & $2.18$ & $4.59$ & $0.38$\\
\hline
\label{tab:Errors}
\end{tabular}
\end{table}
From this table, we can see that the ANN model has a much better predictive capacity than all the analytical models presented previously.The values of $\AARE$ and $\RMSE$ are globally 6 times lower than the best of the analytical models, \ie the Arrhenius model, quoted as reference in the context of hot forming of alloys \cite{Liang-2022}.

@@

Figure \ref{fig:CompInt} shows a comparison, for strain rate $\mdot\varepsilon=1~\ps$, of the flow stresses $\sigma^y$ calculated by the models (as a line) and the experimental results (as points) for the 5 analytical models and the neural network.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/CompInt}
\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=1~\ps$}
\label{fig:CompInt}
\end{figure}
Table \ref{tab:IntVal} shows the $\AARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the 6 strain rates (lines referred as: all) or only on the strain rate $\mdot\varepsilon=1~\ps$.
\begin{table}[h!]
\centering{}
\caption{Accuracy coefficients of interpolation for all models with  $\mdot\varepsilon=1~\ps$}
\begin{tabular}{llcccccc}
	\hline
	$\mdot\varepsilon$               & Coefficients        &   JC    &   MZA   &   HS   &   AR   &  PTM   &  ANN   \\ \hline
	\mr{2}{id. $\mdot\varepsilon$}   & $\AARE(\%)$         & $13.79$ & $20.22$ & $8.57$ & $3.96$ & $5.10$ & $0.70$ \\
	                                 & $\RMSE(\text{MPa})$ & $11.83$ & $19.00$ & $3.97$ & $2.29$ & $4.73$ & $0.38$ \\ \hline
	\mr{2}{$\mdot\varepsilon=1~\ps$} & $\AARE(\%)$         & $14.87$ & $27.79$ & $3.74$ & $1.46$ & $3.16$ & $2.47$ \\
	                                 & $\RMSE(\text{MPa})$ & $12.02$ & $23.67$ & $3.10$ & $1.46$ & $2.65$ & $2.77$ \\ \hline
	\mr{2}{all $\mdot\varepsilon$}   & $\AARE(\%)$         & $14.42$ & $28.90$ & $7.55$ & $3.45$ & $4.90$ & $0.96$ \\
	                                 & $\RMSE(\text{MPa})$ & $11.86$ & $19.86$ & $3.84$ & $2.17$ & $4.45$ & $1.18$ \\ \hline
	\label{tab:IntVal}               &
\end{tabular}
\end{table}

@@

From a general appearance point of view, the other 4 models, HS, AR, PTM and ANN, give globally similar results with a higher fidelity for the AR and ANN models compared to the other two models.
Table \ref{tab:IntVal} shows the quantitative comparison on $\AARE$ and $\RMSE$ for three different cases: on the 5 identified strain rates, on only the strain rate $\mdot\varepsilon=1~\ps$ and on all 6 strain rates for these 6 models.
It appears from this Table that if the two models AR and ANN give equivalent (and excellent) results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=1~\ps$, the ANN model gives globally a better result on the whole of the strain rates with values of $\AARE=0.96\%$ and $\RMSE=1.18~\text{MPa}$ respectively, that is to say values approximately 2 to 3 times lower for the ANN model compared to the AR model.

@@

In this new identification configuration, Figure \ref{fig:CompExt} shows a comparison, for strain rate $\mdot\varepsilon=5~\ps$, of the flow stresses $\sigma^y$ computed by the models (as a line) and the experimental results (as points) for the 5 analytical models and the neural network.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/CompExt}
\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=5~\ps$}
\label{fig:CompExt}
\end{figure}
Table \ref{tab:ExtVal} shows the $\AARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the 6 strain rates (lines referred as: all) or only on the strain rate $\mdot\varepsilon=5~\ps$.
\begin{table}[h!]
\centering{}
\caption{Accuracy coefficients of extrapolation for all models with  $\mdot\varepsilon=5~\ps$}
\begin{tabular}{llcccccc}
\hline
$\mdot\varepsilon$               & Coefficients        & JC      & MZA     & HS     & AR     & PTM     & ANN\\
\hline
\mr{2}{id. $\mdot\varepsilon$}   & $\AARE(\%)$         & $13.09$ & $19.09$ & $7.30$ & $4.03$ & $4.34$  & $0.61$\\
                                 & $\RMSE(\text{MPa})$ & $9.86$  & $16.26$ & $3.36$ & $2.32$ & $3.63$  & $0.32$\\\hline
\mr{2}{$\mdot\varepsilon=5~\ps$} & $\AARE(\%)$         & $20.16$ & $24.27$ & $7.73$ & $3.53$ & $11.46$ & $3.87$\\
                                 & $\RMSE(\text{MPa})$ & $20.73$ & $25.95$ & $7.83$ & $4.02$ & $12.91$ & $5.84$\\\hline
\mr{2}{all $\mdot\varepsilon$}   & $\AARE(\%)$         & $15.12$ & $25.87$ & $7.12$ & $3.86$ & $5.34$  & $1.09$\\
                                 & $\RMSE(\text{MPa})$ & $12.36$ & $18.24$ & $4.43$ & $2.68$ & $6.23$  & $2.40$\\\hline
\label{tab:ExtVal}
\end{tabular}
\end{table}

>>>>

The material used in this study is the modified carbon alloy AISI P20 whose chemical composition is given in Table \ref{tab:Composition}.
\begin{table}[h!]
\centering
\caption{Chemical composition of AISI P20 steel, Fe = balance.}
\begin{tabular}{lccccccc}
	\hline
	Element &  C   &  Mn  &  Mo  &  Si  &  Ni  &  Cr  &  Cu  \\ \hline
	Wt~\%   & 0.30 & 0.89 & 0.52 & 0.34 & 0.68 & 1.86 & 0.17 \\ \hline
\end{tabular}
\label{tab:Composition}
\end{table}
Cylindrical samples were machined with an initial diameter of $d=10$~mm and a height of $h_0=15$~mm.
A batch of 30 hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the 5 temperature levels of $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$ with the 6 strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/Gleeble-3800}
\caption{The Gleeble-3800 thermomechanical simulator system used for this study}
\label{fig:Gleeble3800}
\end{figure}
Thin tantalum sheets were used as a lubricating material at the contact surface of the anvils and samples to minimize friction during testing.
As shown in Figure \ref{fig:GleebleProcess}, the samples were heated to a temperature of $1260\celsius$ with a heating rate of $2$\celsius/s and held at this temperature for $5$~min to eliminate thermal gradients.
They were then cooled down with a rate of $1$\celsius/s to the test temperature and then held at constant temperature for $1$~min before deformation.
During the compression phase, the temperature of the specimen is kept constant by the thermal control system of the machine.
After compression, the specimen is quickly quenched to freeze its microstructure for later analysis.
Figure \ref{fig:GleebleProcess} also shows the aspects of the specimens before and after the compression test: $h_0$ and $r_0$ are the height and radius before compression and $h$, $r_m$ and $r_t$ are the height, large radius and small radius of the specimen after compression, respectively.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.8\columnwidth]{Figures/GleebleProcess}
\caption{Schematic diagram of the experimental process.}
\label{fig:GleebleProcess}
\end{figure}

@@

\begin{table}[h!]
\centering
\caption{Parameters' values of the Johnson-Cook flow law for the P20 steel.}
\begin{tabular}{ccccc}
	\hline
	$A~(\text{MPa})$ & $B~(\text{MPa})$ &   $n$    &   $C$    &   $m$    \\
	   $13.5143$     &     $21.816$     & $0.0746$ & $0.3404$ & $0.7057$ \\ \hline
\end{tabular}
\label{tab:JC}
\end{table}

@@

By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$.
The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively.
Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right),
\end{equation}
with $S_2=C_5+C_6\left(T-T_0\right)$.
Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot\varepsilon/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$.
The parameters of MZA model are given in Table \ref{tab:MZA} while its prediction are plotted in Figure \ref{fig:CompExp-MZA-6}.
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Modified-Zerilli-Armstrong Model}
\begin{tabular}{ccccccc}
	\hline
	  $C_1$   &   $C_2$   &         $C_3$          &         $C_4$          &  $C_5$   &         $C_6$         &   $n$    \\
	$13.5143$ & $21.2591$ & $4.7902\times 10^{-3}$ & $1.4895\times 10^{-4}$ & $0.1389$ & $1.495\times 10^{-4}$ & $0.0621$ \\ \hline
\end{tabular}
\label{tab:MZA}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/CompExp-MZA-6}
\caption{Comparison between the experimental and predicted flow stresses by MZA model}
\label{fig:CompExp-MZA-6}
\end{figure}
It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates.
The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation.
For the MZA model, $\AARE=21.20~\%$ and $\RMSE=19.57~\text{MPa}$, this shows an overall worse performance than the JC model as reported in \cite{TizeMha-2022}.

@@

\begin{table}[h!]
\centering
\caption{Parameters' values of the Hansel-Spittel flow law for the P20 steel.}
\begin{tabular}{ccccc}
	\hline
	        $A$          &         $m_1$          &   $m_2$   &        $m_3$         &         $m_4$         \\
	$5.954\times 10^{3}$ & $-3.3576\times10^{-3}$ & $0.2641$  &      $-0.0868$       & $2.2688\times10^{-4}$ \\ \hline
	                     &         $m_5$          &   $m_6$   &        $m_7$         &         $m_8$         \\
	                     & $-4.2163\times10^{-4}$ & $-0.0561$ & $2.264\times10^{-4}$ &          $0$          \\ \hline
\end{tabular}
\label{tab:HS}
\end{table}

@@

The determination of the order $m$ of the polynomials defined by Equations (\ref{eq:ArA}-\ref{eq:Arn}) is defined according to the ability of the model to represent the non-linear dependence of the stress versus the strain and its generalization.
The values $\ln\!A_i$, $\alpha_i$, $n_i$, and $Q_i$ ($i=0,1,2,3,\cdots,m$) are the coefficients of the polynomials to determine using a regression method.
Setting $m=9$ gives the best results and the corresponding parameters are reported in Table \ref{tab:AR}.
\begin{table}[h!]
\centering
\caption{Parameters' values of the Arrhenius flow law for the P20 steel.}
\begin{tabular}{llll}
	\hline
	\multicolumn{1}{c}{$\alpha_i$}  & \multicolumn{1}{c}{$Q_i~(\times 10^{-6})$} & \multicolumn{1}{c}{$\ln\!A_i$} & \multicolumn{1}{c}{$n_i$}  \\ \hline
	$\alpha_0=0.0407$               & $Q_0=0.467$                                & $A_0=35.8092$                  & $n_0=4.8217$               \\
	$\alpha_1=-0.5167$              & $Q_1=-0.6517$                              & $A_1=-58.822$                  & $n_1=3.2814$               \\
	$\alpha_2=6.3912$               & $Q_2=7.6084$                               & $A_2=740.3303$                 & $n_2=71.5963$              \\
	$\alpha_3=-47.3364$             & $Q_3=-48.016$                              & $A_3=-5.0493\times 10^{3}$     & $n_3=-1.9562\times 10^{3}$ \\
	$\alpha_4=220.0014$             & $Q_4=66.795$                               & $A_4=1.1305\times 10^{4}$      & $n_4=1.4461\times 10^{4}$  \\
	$\alpha_5=-654.4553$            & $Q_5=468.8898$                             & $A_5=2.022\times 10^{4}$       & $n_5=-5.431\times 10^{4}$  \\
	$\alpha_6=1.2421\times 10^{3}$  & $Q_6=-2.3032\times 10^{3}$                 & $A_6=-1.5387\times 10^{5}$     & $n_6=1.1761\times 10^{5}$  \\
	$\alpha_7=-1.4523\times 10^{3}$ & $Q_7=4.3707\times 10^{3}$                  & $A_7=3.1798\times 10^{5}$      & $n_7=-1.4882\times 10^{5}$ \\
	$\alpha_8=952.0619$             & $Q_8=-3.9394\times 10^{3}$                 & $A_8=-2.9725\times 10^{5}$     & $n_8=1.0239\times 10^{5}$  \\
	$\alpha_9=-267.4994$            & $Q_9=1.397\times 10^{3}$                   & $A_9=1.0759\times 10^{5}$      & $n_9=-2.9621\times 10^{4}$ \\ \hline
\end{tabular}
\label{tab:AR}
\end{table}
This modified form of the Arrhenius behavior law allows for accurate and reliable prediction over a wide range of temperatures and strain rates.
Equation (\ref{eq:ArStress}) is finally used to compute the flow stress $\sigma^y$ from the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$:
\begin{equation}
\sigma^y = \frac{1}{\alpha(\varepsilon)} \ln\left\{\left(\frac{\mdot\varepsilon \exp{\left(\frac{Q(\varepsilon)}{RT}\right)}}{A(\varepsilon)}\right)^{\frac{1}{n(\varepsilon)}} + \left[1 + \left(\frac{\mdot\varepsilon \exp{\left(\frac{Q(\varepsilon)}{RT}\right)}}{A(\varepsilon)}\right)^{\frac{2}{n(\varepsilon)}}\right]^{\frac{1}{2}}\right\}
\label{eq:ArStress}
\end{equation}

@@

\begin{table}[h!]
\centering
\caption{Parameters' values of the PTM flow law for the P20 steel.}
\begin{tabular}{llll}
	\hline
	\multicolumn{1}{c}{$A_i$}  & \multicolumn{1}{c}{$B_i$}   & \multicolumn{1}{c}{$C_0^i$} & \multicolumn{1}{c}{$C_1^i$}   \\ \hline
	$A_0=16.8529$              & $B_0=-3.5418\times 10^{-3}$ & $C_0^0=0.1608$              & $C_1^0=-1.9037\times 10^{-5}$ \\
	$A_1=340.6451$             & $B_1=-0.0132$               & $C_0^1=-0.6202$             & $C_1^1=2.67\times 10^{-3}$    \\
	$A_2=-1.9594\times 10^{3}$ & $B_2=-4.4888\times 10^{-3}$ & $C_0^2=4.9516$              & $C_1^2=-3.5788\times 10^{-3}$ \\
	$A_3=4.836\times 10^{3}$   & $B_3=0.2218$                & $C_0^3=-13.1694$            & $C_1^3=-0.0222$               \\
	$A_4=-5.5176\times 10^{3}$ & $B_4=-0.4988$               & $C_0^4=15.25$               & $C_1^4=0.0609$                \\
	$A_5=2.4058\times 10^{3}$  & $B_5=0.3211$                & $C_0^5=-6.587$              & $C_1^5=-0.0413$               \\ \hline
\end{tabular}
\label{tab:PTM}
\end{table}

@@

A summary of the coefficients for evaluating the high-temperature flow stress prediction capability of the AISI P20 alloy for all models presented in this work is reported in Table \ref{tab:Errors}.
\begin{table}[h!]
\centering
\caption{Accuracy coefficients for all the analyzed models.}
\begin{tabular}{lcccccc}
	\hline
	Coefficients        &   JC    &   MZA   &   HS   &   AR   &  PTM   &  ANN   \\ \hline
	$\AARE(\%)$         & $14.05$ & $21.20$ & $7.75$ & $3.56$ & $4.79$ & $0.62$ \\
	$\RMSE(\text{MPa})$ & $12.00$ & $19.57$ & $3.80$ & $2.18$ & $4.59$ & $0.38$ \\ \hline
\end{tabular}
\label{tab:Errors}
\end{table}
From this table, we can see that the ANN model has a much better predictive capacity than all the analytical models presented previously.The values of $\AARE$ and $\RMSE$ are globally 6 times lower than the best of the analytical models, \ie the Arrhenius model, quoted as reference in the context of hot forming of alloys \cite{Liang-2022}.

@@

Figure \ref{fig:CompInt} shows a comparison, for strain rate $\mdot\varepsilon=1~\ps$, of the flow stresses $\sigma^y$ calculated by the models (as a line) and the experimental results (as points) for the 5 analytical models and the neural network.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/CompInt}
\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=1~\ps$}
\label{fig:CompInt}
\end{figure}
Table \ref{tab:IntVal} shows the $\AARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the 6 strain rates (lines referred as: all) or only on the strain rate $\mdot\varepsilon=1~\ps$.
\begin{table}[h!]
\centering{}
\caption{Accuracy coefficients of interpolation for all models with  $\mdot\varepsilon=1~\ps$}
\begin{tabular}{llcccccc}
	\hline
	Strain rate                      & Coefficients        &   JC    &   MZA   &   HS   &   AR   &  PTM   &  ANN   \\ \hline
	\mr{2}{id. $\mdot\varepsilon$}   & $\AARE(\%)$         & $13.79$ & $20.22$ & $8.57$ & $3.96$ & $5.10$ & $0.70$ \\
	                                 & $\RMSE(\text{MPa})$ & $11.83$ & $19.00$ & $3.97$ & $2.29$ & $4.73$ & $0.38$ \\ \hline
	\mr{2}{$\mdot\varepsilon=1~\ps$} & $\AARE(\%)$         & $14.87$ & $27.79$ & $3.74$ & $1.46$ & $3.16$ & $2.47$ \\
	                                 & $\RMSE(\text{MPa})$ & $12.02$ & $23.67$ & $3.10$ & $1.46$ & $2.65$ & $2.77$ \\ \hline
	\mr{2}{all $\mdot\varepsilon$}   & $\AARE(\%)$         & $14.42$ & $28.90$ & $7.55$ & $3.45$ & $4.90$ & $0.96$ \\
	                                 & $\RMSE(\text{MPa})$ & $11.86$ & $19.86$ & $3.84$ & $2.17$ & $4.45$ & $1.18$ \\ \hline
\end{tabular}
\label{tab:IntVal}
\end{table}

@@

From a general appearance point of view, the other 4 models, HS, AR, PTM and ANN, give globally similar results with a higher fidelity for the AR and ANN models compared to the other two models.
Table \ref{tab:IntVal} shows the quantitative comparison on $\AARE$ and $\RMSE$ for three different cases: on the 5 identified strain rates (named id. $\mdot\varepsilon$), on only the strain rate $\mdot\varepsilon=1~\ps$ and on all 6 strain rates for these 6 models.
It appears from this Table that if the two models AR and ANN give equivalent (and excellent) results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=1~\ps$, the ANN model gives globally a better result on the whole of the strain rates with values of $\AARE=0.96\%$ and $\RMSE=1.18~\text{MPa}$ respectively, that is to say values approximately 2 to 3 times lower for the ANN model compared to the AR model.

@@

In this new identification configuration, Figure \ref{fig:CompExt} shows a comparison, for strain rate $\mdot\varepsilon=5~\ps$, of the flow stresses $\sigma^y$ computed by the models (as a line) and the experimental results (as points) for the 5 analytical models and the neural network.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/CompExt}
\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=5~\ps$}
\label{fig:CompExt}
\end{figure}
Table \ref{tab:ExtVal} shows the $\AARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the 6 strain rates (lines referred as: all) or only on the strain rate $\mdot\varepsilon=5~\ps$.
\begin{table}[h!]
\centering{}
\caption{Accuracy coefficients of extrapolation for all models with  $\mdot\varepsilon=5~\ps$}
\begin{tabular}{llcccccc}
	\hline
	Strain rate                      & Coefficients        &   JC    &   MZA   &   HS   &   AR   &   PTM   &  ANN   \\ \hline
	\mr{2}{id. $\mdot\varepsilon$}   & $\AARE(\%)$         & $13.09$ & $19.09$ & $7.30$ & $4.03$ & $4.34$  & $0.61$ \\
	                                 & $\RMSE(\text{MPa})$ & $9.86$  & $16.26$ & $3.36$ & $2.32$ & $3.63$  & $0.32$ \\ \hline
	\mr{2}{$\mdot\varepsilon=5~\ps$} & $\AARE(\%)$         & $20.16$ & $24.27$ & $7.73$ & $3.53$ & $11.46$ & $3.87$ \\
	                                 & $\RMSE(\text{MPa})$ & $20.73$ & $25.95$ & $7.83$ & $4.02$ & $12.91$ & $5.84$ \\ \hline
	\mr{2}{all $\mdot\varepsilon$}   & $\AARE(\%)$         & $15.12$ & $25.87$ & $7.12$ & $3.86$ & $5.34$  & $1.09$ \\
	                                 & $\RMSE(\text{MPa})$ & $12.36$ & $18.24$ & $4.43$ & $2.68$ & $6.23$  & $2.40$ \\ \hline
\end{tabular}
\label{tab:ExtVal}
\end{table}
